Untitled

### 2020-08-27 paper_results.Rmd
update models

    if(length(levels(meals[[i]])) > 2){
      models_meals_uni[[k]] <-  bind_rows(
        mutate(out, level = rns), 
        data_frame(est = 0, se = 0, z = NA, p = NA, 
                   level = paste0(levels(meals[[i]])[1], " (REF)"))
      ) %>%
        mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
    }
    else{
      models_meals_uni[[k]] <- mutate(
        out, level = paste0(rns, " (vs ", levels(meals[[i]])[1], ")")
        ) %>%
        mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
    }

@@

  var_labs <- c("Assistance required", "Diet", "Feeding assistance req.", 
                "Position", "Red tray")

@@

@@

  vars <- c("gender", "age", "cfs", "comorbid", "meds", "must_score", "los", 
            "aes")

@@

    if(class(meals2[[i]]) == "factor"){
      if(length(levels(meals2[[i]])) > 2){
        models_patients_uni[[k]] <-  bind_rows(
          mutate(out, level = rns), 
          data_frame(est = 0, se = 0, z = NA, p = NA, 
                     level = paste0(levels(meals2[[i]])[1], " (REF)"))
        ) %>%
          mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
      }
      else{
        models_patients_uni[[k]] <- mutate(
          out, level = paste0(rns, " (vs ", levels(meals2[[i]])[1], ")")
          ) %>%
          mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
      }
    }
    if(class(meals2[[i]]) == "numeric"){
      models_patients_uni[[k]] <- mutate(out, level = "") %>%
          mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
    }

@@

  var_labs <- c("Female (vs Male)", "Age (years)", "CFS", 
                "Comorbidities", "Number of medications", "MUST", "LOS", 
                "Any adverse events (vs none)")

>>>>

    if(length(levels(meals[[i]])) > 2){
      models_meals_uni[[k]] <-  bind_rows(
        mutate(out, level = rns), 
        data_frame(est = 0, se = 0, z = NA, p = NA, 
                   level = paste0(levels(meals[[i]])[1], " (REF)"))
      ) %>%
        mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
    }
    else{
      models_meals_uni[[k]] <- mutate(out, level = "") %>%
        mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
    }

@@

  var_labs <- c("Assistance required (vs none)", "Diet", 
                "Feeding assistance req. (vs none)", 
                "Position", "Red tray (vs normal tray)")

@@

```
```{r}

  dist_bar_plot(patients, "cfs_cat")

@@

  vars <- c("gender", "age", "cfs", "cfs_cat", "comorbid", "meds", 
            "must_score", "los", 
            "aes")

@@

    if(class(meals2[[i]]) == "factor"){
      if(length(levels(meals2[[i]])) > 2){
        models_patients_uni[[k]] <-  bind_rows(
          mutate(out, level = rns), 
          data_frame(est = 0, se = 0, z = NA, p = NA, 
                     level = paste0(levels(meals2[[i]])[1], " (REF)"))
        ) %>%
          mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
      }
      else{
        models_patients_uni[[k]] <- mutate(out, level = "") %>%
        mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
      }
    }
    if(class(meals2[[i]]) == "numeric"){
      models_patients_uni[[k]] <- mutate(out, level = "") %>%
      mutate(var = i, lrt_p = pvalue, lrt_p_lab = pvalue2)
    }

@@

  var_labs <- c("Female (vs Male)", "Age (years)", "CFS", "CFS Category",
                "Comorbidities", "Number of medications", "MUST", "LOS", 
                "Any adverse events (vs none)")
